Lineage Analysis of CRISPR and shRNA Screens

### 2018-08-23 lineages_18Q3.Rmd
rename heatmaps with clustering metric

Load heatmap matrices:
```{r}
chm_scores <- readRDS("./data_munging/rds/crispr_heatmap_scores.rds")
chm_ge <- readRDS("./data_munging/rds/crispr_heatmap_ge.rds")
chm_mut <- readRDS("./data_munging/rds/crispr_heatmap_mut.rds")
chm_cn <- readRDS("./data_munging/rds/crispr_heatmap_cn.rds")

@@

@@

# chm_scores_c1 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[1]],])))
# chm_scores_c2 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[2]],])))
# chm_scores_c3 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[3]],])))
# chm_scores_c4 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[4]],])))

@@

Code for heatmap of CGC-filtered genes only:
```{r, eval=FALSE}
chm_scores_cgc <- subset(chm_scores, rownames(chm_scores) %in% cgc$Hugo_Symbol)
chm_ge_cgc <- subset(chm_ge, rownames(chm_ge) %in% cgc$Hugo_Symbol)
chm_mut_cgc <- subset(chm_mut, rownames(chm_mut) %in% cgc$Hugo_Symbol)
chm_cn_cgc <- subset(chm_cn, rownames(chm_cn) %in% cgc$Hugo_Symbol)

@@

pdf("./plots_18Q3/crispr_heatmap_all_cgc.pdf", width = 100, height = 100, paper = "special")
draw(chm_all_plot_cgc, heatmap_legend_side = "right", annotation_legend_side = "right")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
dev.off()
```

@@

## Grouped plots {.tabset .tabset-fade .tabset-pills}

```{r fig.height=12, fig.width=12}
makeCRISPRgrob("KRAS")
```

```{r fig.height=12, fig.width=12}
makeCRISPRgrob("TP53")
```

```{r fig.height=12, fig.width=12}
makeCRISPRgrob("BRAF")
```

```{r fig.height=12, fig.width=12}
makeCRISPRgrob("NRAS")
```

>>>>

Load heatmap matrices:
```{r, eval=FALSE}
chm_scores <- readRDS("./data_munging/rds/crispr_heatmap_scores.rds")
chm_ge <- readRDS("./data_munging/rds/crispr_heatmap_ge.rds")
chm_mut <- readRDS("./data_munging/rds/crispr_heatmap_mut.rds")
chm_cn <- readRDS("./data_munging/rds/crispr_heatmap_cn.rds")

@@

#### Euclidean distance

@@

@@

Code for heatmap of CGC-filtered genes only

#### Euclidean distance

```{r, eval=FALSE}
chm_scores_cgc <- subset(chm_scores, rownames(chm_scores) %in% cgc$Hugo_Symbol)
chm_ge_cgc <- subset(chm_ge, rownames(chm_ge) %in% cgc$Hugo_Symbol)
chm_mut_cgc <- subset(chm_mut, rownames(chm_mut) %in% cgc$Hugo_Symbol)
chm_cn_cgc <- subset(chm_cn, rownames(chm_cn) %in% cgc$Hugo_Symbol)

@@

pdf("./plots_18Q3/crispr_heatmap_euclidean_all_cgc.pdf", width = 100, height = 100, paper = "special")
draw(chm_all_plot_cgc, heatmap_legend_side = "right", annotation_legend_side = "right")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
dev.off()
```

#### Pearson correlation

```{r, eval=FALSE}
chm_scores_cgc <- subset(chm_scores, rownames(chm_scores) %in% cgc$Hugo_Symbol)
chm_ge_cgc <- subset(chm_ge, rownames(chm_ge) %in% cgc$Hugo_Symbol)
chm_mut_cgc <- subset(chm_mut, rownames(chm_mut) %in% cgc$Hugo_Symbol)
chm_cn_cgc <- subset(chm_cn, rownames(chm_cn) %in% cgc$Hugo_Symbol)

chm_plot_cgc <- Heatmap(chm_scores_cgc, name = "CERES Score",
        bottom_annotation = HeatmapAnnotation(df = chm_annot),
        bottom_annotation_height = unit(5, "in"),
        row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
        col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
        na_col = "black",
        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
        row_names_gp = gpar(fontsize = 10),
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_names_gp = gpar(fontsize = 8),
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "pearson",
        clustering_distance_columns = "pearson",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(4, "in"),
        row_dend_width = unit(4, "in"),
        width = 3)

pdf("./plots_18Q3/crispr_heatmap_pearson_all_cgc.pdf", width = 100, height = 100, paper = "special")
draw(chm_all_plot_cgc, heatmap_legend_side = "right", annotation_legend_side = "right")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
dev.off()
```

@@

## Grouped plots

Plot code:
```{r, eval=FALSE}
crispr_all_genes <- unique(crispr_data$Hugo_Symbol)
crispr_all_groups <- lapply(crispr_all_genes, makeCRISPRgrob)
crispr_all_groups_paths <- paste0(crispr_all_genes, "_crispr_grouped.png")
pwalk(list(crispr_all_groups_paths, crispr_all_groups), ggsave, path = "./plots_18Q3/crispr_grouped_plots", dpi = 300, width = 12, height = 12, units = "in")
```

Data management:
```{r, eval=FALSE}
crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_grouped_plots", full.names = TRUE))
names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_grouped.png" = "", "./plots_18Q3/crispr_grouped_plots/" = ""))
```

Plots:
```{r, eval=FALSE}
crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))
crispr_all_bygene <- crispr_all_bygene[match(crispr_bygene_order, names(crispr_all_bygene))]
bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
```
